% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Resume},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{Resume}
\author{}
\date{}
\begin{document}
\maketitle


\section{Antonio Vera Gonzalez}\label{antonio-vera-gonzalez}

+1 (208) 760-5871\\
ver21021@byui.edu\\
https://www.linkedin.com/in/antonioverag1212/

\subsection{Relevant Experience}\label{relevant-experience}

\subsubsection{Credit Analyst (Small Business
Oriented)}\label{credit-analyst-small-business-oriented}

\textbf{Edpyme Credivision S.A., Lima, Peru}\\
\emph{January 2021 -- July 2021}

\begin{itemize}
\tightlist
\item
  Built strong relationships with over 35 new clients through constant
  interaction while developing my own portfolio.
\item
  Built a loan portfolio of over S/. 300,000 during the COVID-19
  pandemic.
\item
  Analyzed more than 50 loan requests as a member of the Loan Approval
  Committee.
\end{itemize}

\subsubsection{Student Instructor (GE
101)}\label{student-instructor-ge-101}

\textbf{Brigham Young University--Idaho, Rexburg, ID}\\
\emph{August 2022 -- November 2022}

\begin{itemize}
\tightlist
\item
  Taught classes averaging 25 first-year college students.
\item
  Planned approximately 13 lessons per semester in teams of two or three
  instructors.
\item
  Instructed more than 200 students over five semesters while
  maintaining effective classroom management.
\end{itemize}

\subsubsection{Full-Time Representative}\label{full-time-representative}

\textbf{The Church of Jesus Christ of Latter-day Saints, Mexico City,
Mexico}\\
\emph{June 2018 -- May 2020}

\begin{itemize}
\tightlist
\item
  Led groups of eight representatives in leadership training.
\item
  Managed challenging situations through teamwork, communication, and
  goal setting.
\end{itemize}

\subsubsection{Economic Consulting
Project}\label{economic-consulting-project}

\textbf{Fizz Rizz, Rexburg, ID}\\
\emph{February 2026 -- April 2026}

\begin{itemize}
\tightlist
\item
  Conducted an economic analysis of sales, pricing, and customer
  behavior.
\item
  Used linear regression in R to identify weekly and seasonal sales
  patterns.
\item
  Designed a Power BI presentation to communicate findings and pricing
  recommendations.
\end{itemize}

\subsection{Education}\label{education}

\subsubsection{Brigham Young
University--Idaho}\label{brigham-young-universityidaho}

\textbf{Bachelor of Science in Economics}\\
\emph{January 2022 -- Present}

\begin{itemize}
\tightlist
\item
  Minor in Data Science
\item
  Expected graduation: Fall 2026
\end{itemize}

\subsubsection{Fundet Credit Analyst Intensive
Program}\label{fundet-credit-analyst-intensive-program}

\textbf{Credit Analyst Certification}\\
\emph{January 2021 -- July 2021}

\begin{itemize}
\tightlist
\item
  Completed intensive training for the microfinance sector.
\end{itemize}

\subsubsection{Universidad Nacional Mayor de San
Marcos}\label{universidad-nacional-mayor-de-san-marcos}

\textbf{Economics}\\
\emph{January 2017 -- December 2017}

\begin{itemize}
\tightlist
\item
  Completed coursework in mathematics, politics, and economics.
\item
  Admitted before finishing high school through a competitive entrance
  exam.
\end{itemize}

\subsection{Skills}\label{skills}

\begin{itemize}
\tightlist
\item
  SQL
\item
  Python
\item
  R
\item
  Power BI
\item
  Microsoft Office
\item
  Econometrics
\item
  Statistics
\item
  AI Tools
\end{itemize}

\subsection{Additional Information}\label{additional-information}

\begin{itemize}
\tightlist
\item
  Native Spanish speaker; fluent in English
\item
  Leadership Training at BYU--Idaho \textless!-- \#\#\# Footer
\end{itemize}

Last updated: Jul 2026 --\textgreater{}




\end{document}
